All Gene Supplementary Material - Additional samples removed.

### 2018-01-28 all_gene_analysis/all_gene_analysis_additional_treatment_removed.Rmd
added in aditional scripts

@@

##KEGG analysis
```{r}
# setwd(wd)
# 
# entrez_de <- entrez_geneID_mappings$`[Entrez Gene ID]`[entrez_geneID_mappings$`[Gene ID]` %in% top_ring_ruv$GeneID]
# entrez_de <- entrez_de[entrez_de!="null"]
# entrez_de <- str_split_fixed(entrez_de, pattern = ",", n = 2)[,1]
# 
# kegg <- kegga(entrez_de, species.KEGG="pfa", convert=TRUE)
# kable(topKEGG(kegg, n=Inf))
```

##GO analysis
```{r}
# go <- goana(entrez_de, species.KEGG="pfa", convert=TRUE)
# kable(topGO(go, n=100))
```

>>>>

##Gene set analysis

First we can set up the gene sets after downloading the set annotations from PlasmoDB.
```{r}
MIN_SET_SIZE <- 3

#GO sets
go.data <- fread("./data/PlasmoDB-35_Pfalciparum3D7_GO.gaf", skip = 1, sep="\t",
                         data.table = FALSE)
go.data <- go.data[go.data$V9=="P",] #Looking at biological processes
go.terms <- unique(go.data$V5)
go.gene.sets <- lapply(go.terms, function(go){
  unique(go.data$V2[grepl(go, go.data$V5, fixed = TRUE)])
})
names(go.gene.sets) <- go.terms
go.gene.sets <- go.gene.sets[unlist(lapply(go.gene.sets, length))>=MIN_SET_SIZE]

#KEGG sets
kegg.annot.data <- fread("./data/KEGG_Metacyc_PlasmoDB.csv", 
                         data.table = FALSE)
kegg.annot.data <- kegg.annot.data[kegg.annot.data$`Pathway Source`=="KEGG",]
kegg.gene.sets <- lapply(kegg.annot.data$Genes, 
                         function(x) unique(unlist(str_split(x, " \\| "))))
names(kegg.gene.sets) <- kegg.annot.data$`Pathway Id`
kegg.gene.sets <- kegg.gene.sets[unlist(lapply(kegg.gene.sets, length))>=MIN_SET_SIZE]
```

Enrichment analysis
```{r}
total.genes <- sum(grepl("^PF3D7", rownames(fc2$counts))) #Size of universe
top_genes_set <- top_ring_ruv
go.test <- as.data.frame(do.call("rbind",lapply(go.gene.sets, function(gset){
  set.size <- length(gset)
  gin_all <- gset[gset %in% top_genes_set$GeneID]
  gin_up <- gset[gset %in% top_genes_set$GeneID[top_genes_set$logFC>0]]
  gin_down <- gset[gset %in% top_genes_set$GeneID[top_genes_set$logFC<0]]
  result <- c(set.size=set.size,
              n.both=length(gin_all),
              n.up=length(gin_up),
              n.down=length(gin_down),
              p.value.both=phyper(length(gin_all)-1, m=length(gset), n=total.genes-length(gset),
                                k=nrow(top_genes_set), lower.tail = FALSE),
              p.value.up=phyper(length(gin_up)-1, m=length(gset), n=total.genes-length(gset),
                                k=sum(top_genes_set$logFC>0), lower.tail = FALSE),
              p.value.down=phyper(length(gin_down)-1, m=length(gset), n=total.genes-length(gset),
                                k=sum(top_genes_set$logFC<0), lower.tail = FALSE)
                 )
  return(result)
})))
go.test <- go.test[order(go.test$p.value.both),]

go.test$p.value.both <- format(go.test$p.value.both, scientific=TRUE, digits=3)
go.test$p.value.up <- format(go.test$p.value.up, scientific=TRUE, digits=3)
go.test$p.value.down <- format(go.test$p.value.down, scientific=TRUE, digits=3)
kable(go.test)
```

```{r}
keg.test <- as.data.frame(do.call("rbind",lapply(kegg.gene.sets, function(gset){
  set.size <- length(gset)
  gin_all <- gset[gset %in% top_genes_set$GeneID]
  gin_up <- gset[gset %in% top_genes_set$GeneID[top_genes_set$logFC>0]]
  gin_down <- gset[gset %in% top_genes_set$GeneID[top_genes_set$logFC<0]]
  result <- c(set.size=set.size,
              n.both=length(gin_all),
              n.up=length(gin_up),
              n.down=length(gin_down),
              p.value.both=phyper(length(gin_all)-1, m=length(gset), n=total.genes-length(gset),
                                k=nrow(top_genes_set), lower.tail = FALSE),
              p.value.up=phyper(length(gin_up)-1, m=length(gset), n=total.genes-length(gset),
                                k=sum(top_genes_set$logFC>0), lower.tail = FALSE),
              p.value.down=phyper(length(gin_down)-1, m=length(gset), n=total.genes-length(gset),
                                k=sum(top_genes_set$logFC<0), lower.tail = FALSE)
                 )
  return(result)
})))
keg.test <- keg.test[order(keg.test$p.value.both),]
keg.test$Pathway <- kegg.annot.data$Pathway[match(rownames(keg.test),
                                                  kegg.annot.data$`Pathway Id`)]
kable(keg.test, digits = 4)
```

@@

###Summary Gene Set Plot
```{r}
summary.set.data <- fread("./data/genes_in_set_for_figure2.csv",
                          data.table = FALSE)
gg <- ggplot(summary.set.data, aes(x=Gene, y=`adj-p`, fill=logFC))
# gg <- gg + geom_col() + facet_wrap(~SetName, ncol=1, scales = "free_y", 
#                                                   strip.position = "left")
gg <- gg + geom_col() + facet_grid(SetName ~ ., space = "free_y", scales = "free_y", switch = "y")
gg <- gg + coord_flip() 
gg <- gg + scale_fill_gradient2(low="#0571b0", high = "#ca0020", mid="#ffffff")
gg <- gg + scale_y_continuous(limits = c(0, 0.15))
gg <- gg + theme_bw(base_size = 8) + theme(strip.text.y=element_text(angle=180))
gg <- gg + theme(axis.text.y=element_text(size=4))
gg
```
